\mytitle

### 2012-05-23 papers/SAS2012/implicitization.tex
fixes review 2

>>>>

PAGAI currently neither models the memory heap nor performs interprocedural analysis. Instead, LLVM optimization phases are applied prior to analysis, in order to inline non-recursive function calls and lift certain memory accesses to operations on explicit numerical variables
(e.g. \lstinline|y=t[0]*t[0];| preceded by \lstinline|t[0]=x;| without any aliased write in between is replaced by \lstinline|y=x*x;|).
The remaining memory reads are considered as indeterminates, and memory writes are ignored; this is a sound abstraction.
